An Automatic Verification Framework for Software Configurations

### 2016-05-06 OSDI/learner.tex
config: sec 3, 4 and fig

\section{Learner}

\ennan{This section details how we extract rules from the
intermediate representations. This section should include: 
1) our learning algorithm, 2) how to customize templates,
3) how to input environmental templates, and 4) other methods
for learning rules.}

>>>>

\section{Learner}
\label{sec-learn}

\ennan{This section details how do we extract rules from the
intermediate representations. This section may should have the following
two subsections: Aaron's part (including Xinyu's fine-grained
value correlation rule learning) and Jonathon's part.
In addition, we may need to add one more subsection about
learning system environment information related rules,
\eg, for paths and users.}

### 2016-05-06 OSDI/limit.tex
config: checker part

\para{Legal misconfigurations.}
While \app can check diverse configuration errors without
human participations, all the misconfiguration detection techniques,
including \app, cannot handle some types of configuration errors
resulting from events occurred during system runtime.
Such configuration errors are referred to as {\em legal misconfigurations}%
~\cite{yin11anempirical}. As shown in Yin {\em et al.}%
~\cite{yin11anempirical}, many parameter misconfigurations have 
perfectly legal parameters but do not deliver the functionality intended
by users. These cases are more difficult to detect by
automatic checkers and may require more user training or
better configuration design.
A potential solution is to combine existing misconfiguration diagnosis
tools, \eg, X-ray~\cite{attariyan12x-ray}, 
with \app in order to enhance the 
misconfiguration checking capability.

@@

>>>>

\para{Legal misconfigurations.}
While \app can check diverse configuration errors without
human participations, most of the existing proactive 
misconfiguration detection techniques,
including \app, cannot handle configuration errors
resulting from events occurred during the system runtime.
Such configuration errors are referred to as {\em legal misconfigurations}%
~\cite{yin11anempirical}. In particular, 
many parameter misconfigurations have 
perfectly legal types and values, 
but do not deliver the functionality intended by users. 
For example, after a website's traffic significantly increases,
the parameter {\tt Max\_key\_buffer} in MySQL may not 
be able to handle increasingly more data traffic,
thus leading to the outage of the whole system.
These cases are more difficult to detect by
automatic checkers and may require more user training or
better configuration design.
A potential solution is to combine existing misconfiguration diagnosis
tools, \eg, X-ray~\cite{attariyan12x-ray} 
and ConfAid~\cite{attariyan10automating},
with \app in order to enhance the 
misconfiguration checking capability.

@@

\ennan{One more limitation description here.}

### 2016-05-06 OSDI/motiv.tex

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore}.
For example, both \app and EnCore can handle system execution related
misconfiguration problems.
Furthermore, \app is also able to detect type errors and syntax errors
in configuration files.
\ennan{We may need one example here.}

>>>>

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
For example, both \app and EnCore can handle system execution related
misconfiguration problems.
Furthermore, \app is also able to detect type errors and syntax errors
in configuration files.

### 2016-05-06 OSDI/rel.tex

\para{Configuration languages.}
There have been several language-support efforts proposed to prevent
configuration errors introduced by fundamental deficiencies in
either untyped or low-level languages. For example, in network
configuration management area, it is easy for administrators to
produce configuration errors in their routing configuration files.
PRESTO~\cite{} automates the generation of device-native configurations
with configlets in a template language. 
Loo {\em et al.}~\cite{} adopt Datalog to reason about 
routing protocols in a declarative fashion. COOLAID~\cite{} constructs
a language to describe domain knowledge about network devices and
services to convenient network reasoning and management.

@@

\para{Misconfiguration diagnosis.}
Many misconfiguration diagnosis approaches have been proposed~\cite{}.
For example, ConfAid~\cite{} and X-ray~\cite{} use dynamic information
flow tracking to find possible configuration errors that may result in
failures or performance problems. AutoBash~\cite{} speculatively
executes processes and tracks causality to automatically fix 
misconfigurations. Different from \app, most of misconfiguration
diagnosis efforts aim at finding out errors after the system
failures occur, which typically lead to prolonged recover time.

\para{Misconfiguration tolerance.}
There have been several efforts proposed to test whether systems are 
tolerant to misconfigurations~\cite{xu13do}. 
ConfErr~\cite{} uses a human error hodel from psychology and
linguistics to inject misconfigurations into systems.
SPEX~\cite{xu13do} takes a white-box testing approach to automatically
extract configuration parameter constraints from source code and generates 
misconfigurations to test whether systems can tolerate the potential
configuration errors.

>>>>

\para{Configuration languages.}
There have been several language-support efforts proposed to prevent
configuration errors introduced by fundamental deficiencies in
either untyped or low-level languages. For example, in network
configuration management area, it is easy for administrators to
produce configuration errors in their routing configuration files.
PRESTO~\cite{enck07configuration} 
automates the generation of device-native configurations
with configlets in a template language. 
Loo {\em et al.}~\cite{loo05declarative} adopt Datalog to reason about 
routing protocols in a declarative fashion. 
COOLAID~\cite{chen10declarative} constructs
a language to describe domain knowledge about network devices and
services to convenient network reasoning and management.

@@

\para{Misconfiguration diagnosis.}
Many misconfiguration diagnosis approaches have been proposed%
~\cite{attariyan10automating, attariyan12x-ray}.
For example, ConfAid~\cite{attariyan10automating} 
and X-ray~\cite{attariyan12x-ray} use dynamic information
flow tracking to find possible configuration errors that may result in
failures or performance problems. AutoBash~\cite{su07autobash} 
speculatively
executes processes and tracks causality to automatically fix 
misconfigurations. Different from \app, most of misconfiguration
diagnosis efforts aim at finding out errors after the system
failures occur, which typically lead to prolonged recover time.

\para{Misconfiguration tolerance.}
There have been several efforts proposed to test whether systems are 
tolerant to misconfigurations~\cite{xu13do}. 
%ConfErr~\cite{} uses a human error hodel from psychology and
%linguistics to inject misconfigurations into systems.
SPEX~\cite{xu13do} takes a white-box testing approach to automatically
extract configuration parameter constraints from source code and generates 
misconfigurations to test whether systems can tolerate the potential
configuration errors.
